\bf Forecast reconciliation: A geometric view with new insights on bias correction

### 2020-02-01 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
removed daggers

Table~\ref{tab:Results_MSE} reports both RMTSE and RMATE for 1-step-ahead forecasts.\footnote{{\color{blue} Results and conclusions that follow are almost identical for the other longer forecast horizons. We do not present these here to save space but they are available in an online supplement.}}  An asterisk ($^\ast$) indicates that forecasts are significantly different from the biased base forecasts, while a dagger ($^\dag$) indicates that the unbiased forecasts are significantly different from the biased forecasts from the same reconciliation method $q$. Statistical significance of the differences in the forecast errors is based on the non-parametric Friedman and post-hoc Nemenyi tests, at a 5\% level of significance \citep{HolEtAl2013}. The Friedman test first establishes whether at least one of the forecasts is significantly different from the rest. If this is the case, we use the Nemenyi test to identify groups of forecasts for which there is no evidence of statistically significant differences. This testing approach does not impose any distributional assumptions and does not require multiple pairwise testing between forecasts, which would distort the outcome of the tests. We use the implementation of the tests available in the \verb"tsutils " \citep{tsutils} package for R.}

\begin{table}[!b]
{\color{blue}
\caption {{\color{blue} RMATE and RMTSE} of $1$-step-ahead forecasts from log and Box-Cox transformed series. Biased denotes forecasts from simply reversing the transformation via Eq.~\eqref{eq:BoxCox_back-transformation}. Unbiased(Method-1) performs bias adjustment via a Taylor series expansion as shown in Eq.~\eqref{eq:BoxCox_BT_biasadj} whereas Unbiased(Method-2) bias adjusts by subtracting the in-sample forecast error mean.}
\label{tab:Results_MSE}
\setlength{\tabcolsep}{7pt}
\centering
  \begin{tabular}{ld{3.2}d{3.2}d{3.2}d{3.2}d{3.2}d{3.2}}
    \toprule
    \multicolumn{1}{c}{ } & \multicolumn{3}{c}{Log Transformation} &
    \multicolumn{3}{c}{Box-Cox Transformation}\\
    \cmidrule(lr){2-4} \cmidrule(lr){5-7}
    Method & \multicolumn{1}{c}{Biased} & \multicolumn{1}{c}{Unbiased} & \multicolumn{1}{c}{Unbiased} & \multicolumn{1}{c}{Biased} & \multicolumn{1}{c}{Unbiased} & \multicolumn{1}{c}{Unbiased} \\
    & & \multicolumn{1}{c}{(Method-1)} & \multicolumn{1}{c}{(Method-2)} && \multicolumn{1}{c}{(Method-1)} &\multicolumn{1}{c}{(Method-2)}\\ \midrule
              & \multicolumn{6}{c}{RMATE}\\\cmidrule(lr){2-7}
    Base      & 1.00        & 0.58^{\ast\dag} & 1.40^{\ast\dag} & 1.00        & 0.73^{\ast\dag} & 1.38^{\ast\dag}\\
    OLS       & 0.63^{\ast} & 0.54^{\ast}     & 0.76^{\dag}     & 0.65^{\ast} & 0.67^{\ast}     & 0.86 \\
    MinT      & 0.77^{\ast} & 0.57^{\ast\dag} & 1.15^{\dag}     & 0.77^{\ast} & 0.70^{\ast}     & 1.09^{\dag}\\
    Bottom-up & 1.76^{\ast} & 0.69^{\ast\dag} & 2.72^{\ast\dag} & 1.73        & 0.84^{\ast\dag} & 2.57^{\ast\dag}\\
              & \multicolumn{6}{c}{RMTSE}\\\cmidrule(lr){2-7}
    Base      & 1.00 & 0.99 & 1.01 & 1.00 & 0.98 & 1.04\\
    OLS       & 0.97^{\ast} & 0.96^{\ast} & 0.98^{\ast} & 0.97^{\ast} & 0.96^{\ast} & 1.01\\
    MinT      & 0.97^{\ast} & 0.93^{\ast} & 1.03 & 0.93^{\ast} & 0.91^{\ast} & 0.99\\
    Bottom-up & 1.42 & 1.18 & 1.80 & 1.35 & 1.16 & 1.63\\
    \bottomrule
  \end{tabular}
}    {\color{blue} $^\ast$ indicates a statistically significant difference from the biased base forecasts.$^\dag$ indicates a statistically significant difference from the biased forecasts from the same reconciliation method (same row).}

@@

{\color{blue} Also  of interest is the fact that reconciliation can to some extent mitigate bias even without bias correction.  In particular, using OLS reconciliation without bias correction leads to a statistically significant reduction in bias relative to base forecasts.  This is likely to occur since the direction of bias lies in a direction that is close to orthogonal to the coherent subspace.  Projection therefore eliminates this bias to some extent.}{\color{red} I now see that maybe the daggers should go since we are not talking about them. Please feel free to remove.}.

>>>>

Table~\ref{tab:Results_MSE} reports both RMTSE and RMATE for 1-step-ahead forecasts.\footnote{{\color{blue} Results and conclusions that follow are almost identical for the other longer forecast horizons. We do not present these here to save space but they are available in an online supplement.}}  An asterisk ($^\ast$) indicates that forecasts are significantly different from the biased base forecasts.%, while a dagger ($^\dag$) indicates that the unbiased forecasts are significantly different from the biased forecasts from the same reconciliation method $q$. 
Statistical significance of the differences in the forecast errors is based on the non-parametric Friedman and post-hoc Nemenyi tests, at a 5\% level of significance \citep{HolEtAl2013}. The Friedman test first establishes whether at least one of the forecasts is significantly different from the rest. If this is the case, we use the Nemenyi test to identify groups of forecasts for which there is no evidence of statistically significant differences. This testing approach does not impose any distributional assumptions and does not require multiple pairwise testing between forecasts, which would distort the outcome of the tests. We use the implementation of the tests available in the \verb"tsutils " \citep{tsutils} package for R.}

\begin{table}[!b]
{\color{blue}
\caption {{\color{blue} RMATE and RMTSE} of $1$-step-ahead forecasts from log and Box-Cox transformed series. Biased denotes forecasts from simply reversing the transformation via Eq.~\eqref{eq:BoxCox_back-transformation}. Unbiased(Method-1) performs bias adjustment via a Taylor series expansion as shown in Eq.~\eqref{eq:BoxCox_BT_biasadj} whereas Unbiased(Method-2) bias adjusts by subtracting the in-sample forecast error mean.}
\label{tab:Results_MSE}
\setlength{\tabcolsep}{7pt}
\centering
  \begin{tabular}{ld{3.2}d{3.2}d{3.2}d{3.2}d{3.2}d{3.2}}
    \toprule
    \multicolumn{1}{c}{ } & \multicolumn{3}{c}{Log Transformation} &
    \multicolumn{3}{c}{Box-Cox Transformation}\\
    \cmidrule(lr){2-4} \cmidrule(lr){5-7}
    Method & \multicolumn{1}{c}{Biased} & \multicolumn{1}{c}{Unbiased} & \multicolumn{1}{c}{Unbiased} & \multicolumn{1}{c}{Biased} & \multicolumn{1}{c}{Unbiased} & \multicolumn{1}{c}{Unbiased} \\
    & & \multicolumn{1}{c}{(Method-1)} & \multicolumn{1}{c}{(Method-2)} && \multicolumn{1}{c}{(Method-1)} &\multicolumn{1}{c}{(Method-2)}\\ \midrule
              & \multicolumn{6}{c}{RMATE}\\\cmidrule(lr){2-7}
    Base      & 1.00        & 0.58^{\ast} & 1.40^{\ast} & 1.00        & 0.73^{\ast} & 1.38^{\ast}\\
    OLS       & 0.63^{\ast} & 0.54^{\ast}     & 0.76     & 0.65^{\ast} & 0.67^{\ast}     & 0.86 \\
    MinT      & 0.77^{\ast} & 0.57^{\ast} & 1.15^{\dag}     & 0.77^{\ast} & 0.70^{\ast}     & 1.09\\
    Bottom-up & 1.76^{\ast} & 0.69^{\ast} & 2.72^{\ast} & 1.73        & 0.84^{\ast} & 2.57^{\ast}\\
              & \multicolumn{6}{c}{RMTSE}\\\cmidrule(lr){2-7}
    Base      & 1.00 & 0.99 & 1.01 & 1.00 & 0.98 & 1.04\\
    OLS       & 0.97^{\ast} & 0.96^{\ast} & 0.98^{\ast} & 0.97^{\ast} & 0.96^{\ast} & 1.01\\
    MinT      & 0.97^{\ast} & 0.93^{\ast} & 1.03 & 0.93^{\ast} & 0.91^{\ast} & 0.99\\
    Bottom-up & 1.42 & 1.18 & 1.80 & 1.35 & 1.16 & 1.63\\
    \bottomrule
  \end{tabular}
}    {\color{blue} $^\ast$ indicates a statistically significant difference from the biased base forecasts.}

@@

{\color{blue} Also  of interest is the fact that reconciliation can to some extent mitigate bias even without bias correction.  In particular, using OLS reconciliation without bias correction leads to a statistically significant reduction in bias relative to base forecasts.  This is likely to occur since the direction of bias lies in a direction that is close to orthogonal to the coherent subspace.  Projection therefore eliminates this bias to some extent.}
